\documentclass[a4paper,12pt]{report}

% input/text packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb}
\usepackage{calc}

% graphical/layout packages
\usepackage[top=1in, bottom=1.5in, left=1in, right=1in]{geometry}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{rotating}
\setlist[itemize]{noitemsep, topsep=0pt}
\setlist[enumerate]{itemsep=0pt, topsep=0pt}

%Set graphics path
\graphicspath{ {img/} }

% Horizontal rule with negative spacing
\newcommand{\spacerule}[1]{\vspace{-.66\baselineskip}\rule{#1}{.4pt}\par}

% Group members together to keep title code clean
\newcommand{\membergroup}[4]{%
    \begin{member}{\raggedright}#1\par\spacerule{\widthof{#1}} #2\end{member}\hfill%
        \begin{member}{\raggedleft}#3\par\spacerule{\widthof{#3}} #4\end{member}%
            \par\vspace{\baselineskip}}

% Simple minipage for listing project members
\newenvironment{member}[1]{\begin{minipage}[t]
    {.3\textwidth}#1}{\end{minipage}}

\input{abbreviations.tex}

\begin{document}

\begin{titlepage}
    \input{title.tex}
\end{titlepage}

 \begin{abstract}
 Gamification is gradually finding its way into every corner of online society. E-commerce, social networks and others are quickly adopting these techniques for encouraging and coercing users to stay on their services.

 Recent developments suggest that gamification could be used in the education of programmers as well, and some projects have been made to demonstrate the usefulness of specific techniques already. Here, a more general platform that enables teachers and researchers to put techniques to the test is developed.

 To keep the code maintainable, a modularized structure was employed wherein three larger components interact in a loosely-coupled manner. By doing so, the different parts should be possible to scale horizontally and replace if needed.

 At the end of the development, the site would work fine for simpler programming courses where the focus of the course regards learning a specific language or paradigm. However, some of the core features that are essential to deeper analysis still need to be implemented to unlock the full potential of the platform.
 
 \end{abstract}

\tableofcontents{}

% NOTE: \addtocontents need to keep this format for the toc to be properly columnized
\addtocontents{toc}{\protect\begin{multicols}{2}}

 \input{intro/intro.tex}
 \input{design/design.tex}
 \input{working_methods/working_methods.tex}
 \input{discussion/discussion.tex}
 \input{future_work/future_work.tex}
 \input{appendices/appendices.tex}

\addtocontents{toc}{\protect\end{multicols}}

\end{document}
