\label{sec:social}
Social games are special in the way that they shift game focus from the content to the participants. One could compare the experiences found in these games with the types of experiences found in traditional boardgames, where people sit at an arm's length and socialize as much as they game. Since humans are social animals, the usefulness of these kinds of games should naturally be evaluated further.

An example from the industry is FarmVille\cite{farmville}, where the user-experience is built around social interaction and the challenges mostly consist of simpler farming tasks. There, users spend their time farming crops on their digital gardens in hope that other users will visit and interact with their gardens, yielding more rewards to the owner. In comparison, social games on the gamified programming platform could employ a similar approach, where users spend their time writing code in their digital libraries and let other users look at the code for a fee.

Similarly, many games---traditional and otherwise---make heavy use of cooperation to motivate players. In some games, players are pitted against a common enemy or issue, and are then tasked with beating it. This has the effect of separating the common progress from the individual progress, meaning that weaker players, who might have trouble contributing, and risk getting bored, get some extra motivation and carry on. Simultaneously, stronger players get to see their progress shine as they push progress forward and advance the common progress, which motivates them to deliver even more.

The challenge with such elements is to avoid giving the weak players too much information about the strong players, as this may act as a demotivator. That is, the weak player observes the progress of the strong player, looks at the difference and decides that too much work is required to catch up. By offering a solid framework for creating elements like these, with powerful options for displaying information and smart tools for showing common progress to each and every user, these kinds of demotivators could be studied in detail.
% * explain concepts to others, forcing them to learn;
% * Put their studying in a greater context, should the total progress be shown;
% * find friends and peers to
%    * study with
%    * trade with, if some game currency were to be implemented
%    * "visit" if set in a context like farmville
